---
title: Howe Sound's vascular plant diversity
weight: 1
knit: (function(input, ...) { source(here::here("R/knit_render.R"), local = TRUE)$value(input, ...) })
---

```{r, echo=FALSE, warning=FALSE}
options(error = rlang::entrace, rlang_backtrace_on_error = "full")
library(tidyverse)
message(getwd())
plants <- read.csv("tabular_data/Howe_Sound_vascular_plant_records_consolidated_2024-11-14.csv")
plant.summary <- read.csv("tabular_data/vascular_plant_summary_resynthesized_2024-11-14.csv")
new <- plant.summary %>% filter(str_detect(reportingStatus, "new")) 
confirmed <- plant.summary %>% filter(reportingStatus == 'confirmed') 
reported <- plant.summary %>% filter(reportingStatus == 'reported') 
observed <- plant.summary %>% filter(iNatObservationStatus == 'observed') 
```
Over one thousand vascular plant species are known to occur within the ?tl??a7tsem/Howe Sound Biosphere, represented by `r nrow(plants)` occurrence records. This diverse flora spans nine biogeoclimatic units, from lowland coastal western hemlock forests and associated woodland communities to high elevation subalpine and alpine plant communities.

```{r, echo = FALSE, message=FALSE}
source("scripts/Vascular_BEC_map_mapbox.R")
speciesMap
```

Explore the region's flora by selecting from the biogeoclimatic units displayed on the map:

* Alpine Tundra zone ([CMAunp](#region:CMAunp))
* Mountain Hemlock zone ([MHmm1](#region:MHmm1), [MHmm2](#region:MHmm2))
* Coastal Western Hemlock zone ([CWHdm](#region:CWHdm), [CWHds1](#region:CWHds1), [CWHms1](#region:CWHms1), [CWHvm1](#region:CWHvm1), [CWHvm2](#region:CWHvm2), [CWHxm1](#region:CWHxm1))